% This is based on the LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
% See http://www.springer.com/computer/lncs/lncs+authors?SGWID=0-40209-0-0-0
% for the full guidelines.
%
%
%     To submit at ISWC 2018 - Resource Track
%
%
\documentclass{llncs}

\hyphenation{do-cu-ment do-cu-ments}

\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{comment}
\usepackage{xspace}
\usepackage[usenames, dvipsnames]{xcolor}
\definecolor{igual}{rgb}{0.21, 0.11, 0} 
\usepackage{hyperref}
\definecolor{dark-blue}{rgb}{0.0,0.0,0.1}
\definecolor{dark-green}{rgb}{0.0,0.1,0.0}
\definecolor{dark-red}{rgb}{0.1,0.0,0.0}
\hypersetup{
    colorlinks, linkcolor={dark-red},
    citecolor={dark-green}, urlcolor={dark-blue},
    pdftitle={VoxEL: A Benchmark Dataset for Multilingual Entity Linking},    % title
    pdfauthor={Henry Rosales-Méndez, Aidan HoganBarbara Poblete},     % author
    pdfsubject={LD4IE 2017},   % subject of the document
    pdfkeywords={multilingual;} {entity linking;} {information extraction;}, % list of keywords
}
\usepackage{amsmath}
\newcommand{\argmin}{\arg\!\min}
\newcommand{\argmax}{\arg\!\max}

%para el simbolo de chequeado
\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\usepackage{booktabs} 
\usepackage{multirow}

\newcommand{\ah}[1]{{\color{blue}\textsc{ah:} #1}}

\usepackage{soul} %middleline
\usepackage{pgfplots}
\begin{document}

\title{VoxEL: A Benchmark Dataset for \\Multilingual Entity Linking}
%
\titlerunning{VoxEL: A Benchmark Dataset for Multilingual Entity Linking}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Henry Rosales-M\'endez, Aidan Hogan and Barbara Poblete}
%
\authorrunning{Rosales-Méndez et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
%Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{IMFD Chile \& Department of Computer Science, University of Chile \\
\texttt{\{hrosales,ahogan,bpoblete\}@dcc.uchile.cl}}

\newcommand{\ds}{\textsc{VoxEL}\xspace}

\maketitle              % typeset the title of the contribution
\begin{abstract}
%The Entity Linking (EL) task identify the entities mentions in a text corpus and associate them with corresponding entries in a knowledge base. Most EL approaches are suitable in the English context, but current trends are focused on agnostic-language approaches that allow us to perform EL over texts in many languages. One of the obstacles in multilingual contexts is that publicly available resources are scarce in multilingual contexts. This constitutes a hinder to achieve evaluation the quality of multilingual EL approaches, therefore, it is difficult to achieve progress in the area. In this work we propose VoxEL, a multilingual gold standard manually annotated that involve five languages that aim to favor the evaluation multilingual processes in EL. We also explore the behavior of state of the art of multilingual EL according to VoxEL and propose a new perspective to achieve multilingual annotations through automatic translation.

The Entity Linking (EL) task identifies entity mentions in a text corpus and associates them with corresponding entities in a given knowledge base. While traditional EL approaches have largely focused on English texts, current trends are towards language-agnostic or otherwise multilingual approaches that can perform EL over texts in many languages. One of the obstacles to ongoing research on multilingual EL is a scarcity of annotated datasets with the same text in different languages. In this work we thus propose \ds: a manually-annotated gold standard for multilingual EL featuring the same text expressed in five European languages. We first motivate and describe the \ds dataset, using it to compare the behavior of state of the art EL (multilingual) systems for five different languages, contrasting these results with those obtained using machine translation to English. Overall, our results identify how five state-of-the-art multilingual EL systems compare for various languages, how the results of different languages compare, and further suggest that machine translation of input text to English is now a competitive alternative to dedicated multilingual EL configurations.%. We then present the results of experiments using this dataset to compare the behavior of state of the art of (multilingual) EL systems across the five different languages, additionally comparing these results with methods using machine translation to English.
\keywords{Multilingual, Entity Linking, Information Extraction}\\
\textbf{Resource type}: Dataset\\
\textbf{Permanent URL}: \url{https://dx.doi.org/10.6084/m9.figshare.6539675}
\end{abstract}

\section{Introduction} 
\label{sec:intro}

%There is a large amount of textual information available in an unstructured format, that is understandable to humans but difficult to process automatically by machine. 
%The vast amount of unstructured textual information available makes it impossible to assimilate for human beings, so automatic techniques are necessary to process it. In this context, Entity Linking (EL) is a task of Information Extraction (IE) that aim to bring some notion of \textcolor{red}{structure} in textual corpora, identifying and linking entities in the text with their corresponding knowledge-base entries. 

The Entity Linking (EL) task identifies entity mentions in a text corpus and associates them with corresponding entities in a Knowledge Base (KB). In this way, we can leverage the information of publicly available KBs about real-world entities to achieve a better understanding of their semantics and also of natural language. For instance, in the text \textit{``in the world of pop music, there is Michael Jackson and there is everybody else''} quoted from The New York Times, we can link the mention \textit{Michael Jackson} with its corresponding entry in, e.g., the Wikidata KB~\cite{Wikidata_vrandevcic2014wikidata} (\url{wd:Q2831}), or the DBpedia KB~\cite{dbpedia-lehmann2015dbpedia} (\url{dbr:Michael_Jackson})\footnote{Throughout, we use prefixes according to \url{http://prefix.cc}.} allowing us to leverage, thereafter, the information in the KB about this entity to support semantic search, relationship extraction, text enrichment, entity summarisation, or semantic annotation, amongst other applications.

One of the major driving forces for research on EL has been the development of a variety of ever-expanding KBs that describe a broad selection of notable entities covering various domains (e.g., Wikipedia, DBpedia, Freebase, YAGO, Wikidata). Hence, while traditional Named Entity Recognition (NER) tools focused on identifying mentions of entities of specific types in a text, EL further requires disambiguation of which entity in the KB is being spoken about; this remains a challenging problem. On the one hand, name variations -- such as \textit{``Michael Joseph Jackson''}, \textit{``Jackson''}, \textit{``The King of Pop''} -- mean that the same KB entity may be referred to in a variety of ways by a given text. On the other hand, ambiguity -- where the name \textit{``Michael Jackson''} may refer to various (other) KB entities, such as a journalist (\texttt{wd:Q167877}), a football player (\texttt{wd:Q6831558}), an actor (\texttt{wd:Q6831554}), amongst others -- means that an entity mention in a text may have several KB candidates associated with it.

%Another problem concerning to EL is the lack of consensus about the concept of ``entity''\cite{Borrega2007}. Some definitions of entity have been proposed in the literature by different areas of Natural Language Processes to response \textit{``what is an entity?''} but still remain an open issue~\cite{ourAMW2018}. As consequence, to decide when to select or not a mention for the annotation process is unclear in EL, as well as the inclusion or not of annotations in gold standards for evaluation purposes. In order to lessen this phenomenon Jha et al.~\cite{Jha2017} proposes a set of desirable properties that a gold standard must satisfy. On the other hand, \textcolor{red}{as we show in our previous work~\cite{ourAMW2018}}, we advocate for a more practical point of view inherent to EL that takes into account the domain of application rather a semantic perspective. Therefore, we encourage to answer better the question \textit{``what should Entity Linking link?''}. For Instance, coreferences are not so important if we want to find all documents about US singers, but relevant in extraction relation scenarios where many relations may be expressed in text with pronouns. \textcolor{red}{Two versions of this desirable behavior (relaxed and strict) would be fairer}. The popular EL system Babelfy\cite{Babelfy-moro2014entity} implements this criterion allowing us to specify if we only wish to annotate Proper Names, or include also concepts such as belt, bed, chair, table, etc.

 
Many research works have addressed these challenges of the EL task down through the years. Most of the early EL systems proposed in the literature were monolingual approaches focusing on texts written in one single language, in most cases English (e.g., \cite{mendes2011dbpedia,aida2011}). These approaches often use resources of a specific language, such as Part-Of-Speech taggers and WordNet\footnote{\url{https://wordnet.princeton.edu}; April 1st, 2018}, which prevent generalisation or adaptation to other languages. Furthermore, most of the labelled datasets available for training and evaluating EL approaches were English only (e.g., AIDA/CoNLL~\cite{aida2011}, DBpedia Spotlight Corpus~\cite{mendes2011dbpedia}, KORE 50~\cite{kore50}). 

However, as the EL area has matured, more and more works have begun to focus on languages other than English, including multilingual approaches that are either language agnostic~\cite{THD-dojchinovski2012recognizing,daiber2013improving,ferragina2010tagme,mag2017} -- relying only on the language of labels available in the reference KB -- or that can be configured for multiple languages~\cite{Babelfy-moro2014entity,freme-ner2016}. Recognising this trend, a number of multilingual datasets for EL were released, such as for the 2013 TAC KBP challenge\footnote{\url{https://tac.nist.gov/2013/KBP/}; April 1st, 2018} %, NTCIR\footnote{\url{http://ntcir.nii.ac.jp/CrossLink/}; April 1st, 2018} 
and the 2015 SemEval Task 13 challenge\footnote{\url{http://alt.qcri.org/semeval2015/task13/}; April 1st, 2018}. Although such resources are valuable for multilingual EL research -- where in previous work~\cite{Rosales-MendezP17} we presented an evaluation of EL systems comparing two languages from the SemEval dataset -- they have their limitations, key amongst which are their limited availability (participants only\footnote{We have managed to acquire the SemEval dataset, but unfortunately we were not able to acquire the TAC--KBP dataset: our correspondence was not responded to.}), a narrow selection of languages, and differences in text and annotations across languages that makes it difficult to compare the performance in each language. More generally, the EL datasets available in multiple languages -- and languages other than English -- greatly lags behind what is available for English.

\paragraph{Contributions:} In this paper, we propose the \textsc{VoxEL} dataset: a manually-annotated gold standard for EL considering five European languages, namely German, English, Spanish, French and Italian. This dataset is based on an online source of multilingual news, where we selected and annotated 15 corresponding news articles for these five languages (75 articles in total). Additionally, we created two versions of \textsc{VoxEL}: a \textit{strict} version where entities correspond to a restricted definition of entity, as a mention of a person, place or organisation (based on traditional MUC/NER definitions), and a \textit{relaxed} version where we considered a broader selection of mentions referring to entities described by Wikipedia. Based on the \textsc{VoxEL} dataset, using the GERBIL evaluation framework~\cite{gerbil-2015}, we present results for various EL systems, allowing us to compare not only across systems, but also across languages. As an additional contribution, we compare the performance of EL systems configurable for a given language with the analogous results produced by applying state-of-the-art machine translation (Google translate) to English and then applying EL configured for English. Our findings show that most systems perform best for English text. Furthermore, machine translation of input text to English achieves comparable -- and often better -- performance when compared with dedicated multilingual EL approaches. 

%\paragraph{Outline:} Section \ref{subsect:preliminaries} introduces preliminaries relating to the Entity Linking task. Section~\ref{sec:relatedWork} discusses works that have address the problem of multilingual Entity Linking, including discussion of both systems and datasets. Section~\ref{sec:voxel} presents the design and creation of the \textsc{VoxEL} dataset, along with some descriptive statistics. Section~\ref{sec:exp} presents some research questions that can be addressed with \textsc{VoxEL}, and presents corresponding experiments over a selection of EL systems. We then conclude and discuss future directions in Section~\ref{sec:conclusion}.


\section{Preliminaries}
\label{subsect:preliminaries}

We first introduce some preliminaries relating to EL. Let $E$ be a set of entity identifiers in a KB; these are typically IRIs, such as \texttt{wd:Q2831}, \texttt{dbr:Michael\_Jackson}. Given an input text, the EL process can be conceptualised in terms of two main phases. First, Entity Recognition (ER) establishes a set of entity mentions $M$, where each such mention is a sub-string referring to an entity, annotated with its start position in the input text, e.g., $(37,\textit{``Michael Jackon''})$. Second, for each mention $m\in{}M$ recognised by the first phase, Entity Disambiguation (ED) attempts to establish a link between $m$ and the corresponding identifier $e\in{}E$ for the KB entity to which it refers. The second disambiguation phase can be further broken down into a number of (typical) sub-tasks, described next:

\begin{description}
\item \textit{Candidate entity generation}:
For each mention $m\in{}M$, this stage selects a subset of the most probable KB entities $E_m \subseteq E$ to which it may refer. There are two high-level approaches by which candidate entities are often generated. The first is a dictionary-based approach, which involves applying keyword or string matching between the mention $m$ and the label of entities from $E$. The second is an NER-based approach, where traditional NER tools are used to identify entity mentions (potentially) independently of the KB. 

\item \textit{Candidate entity ranking}: This stage is where the final disambiguation is made: the candidate entities $E_m$ for each mention $m$ are ranked according to some measure indicating their likelihood of being the reference for $m$. The measures used for ranking each entity $e \in E_m$ may take into account features of the candidate entity $e$ (e.g., centrality), features of the candidate link $(m,e)$ (e.g., string similarity), features involving $e$ and candidates for neighbouring mentions $E_m'$ (e.g., graph distance in the KB), and so forth. Ranking may take the form of an explicit metric that potentially combines several measures, or may be implicit in the use of machine-learning methods that classify candidates, or that compute an optimal assignment of links.

\item \textit{Unlinkable mention prediction}: The target KBs considered by EL are often, by their nature, incomplete. In some applications, it may thus be useful to extract entity mentions from the input text that do not (yet) have a corresponding entity in the KB. These are sometimes referred to as \textit{emerging entities}, are typically produced by NER candidate generation (rather than a dictionary approach), and are assigned a label such as \textit{NIL} (Not In Lexicon). 
\end{description}

It is important to note that while the above processes provide a functional overview of the operation of most EL systems, not all EL systems follow this linear sequence of steps. Most systems perform recognition first, and once the mentions are identified the disambiguation phase is initiated~\cite{mendes2011dbpedia,Babelfy-moro2014entity}. However, other approaches may instead apply a unified process, building models that create feedback between the recognition and disambiguation steps~\cite{fahrni2012hits}. In any case, the output of the EL process will be a set of links of the form $(m,e)$, where the mention $m$ in the text is linked to the entity $e$ in the KB, optionally annotated with a confidence score -- often called a \textit{support} --  for the link.


%===============================================================
\section{Related Work}
\label{sec:relatedWork}

We now cover related works in the context of multilingual EL, first discussing approaches and systems, thereafter discussing available datasets.

%-----------------------------------------------------------
\subsection{Multilingual EL Systems}
%.................
%% 1) HABLAR COSAS DE MULTILINGUAL
In theory, any EL system can be applied to any language; as demonstrated in our previous work~\cite{Rosales-MendezP17}, even a system supporting only English may still be able to correctly recognise and link the name of a person such as \textit{Michael Jackson} in the text of another language, assuming the alphabet remains the same. Hence, the notion of a multilingual EL system can become blurred. For example language-agnostic systems -- systems that require no linguistic components or resources specific to a language -- can become multilingual simply by virtue of having a reference KB with labels in a different -- or multiple different -- language(s). 

Here we thus focus on EL systems that have published evaluation results over texts from multiple languages\footnote{This excludes systems such as Apache Stanbol, OpenCalais, PoolParty, etc.}, thus demonstrating proven multilingual capabilities. We summarise such systems in Table \ref{tab:multilingual_approaches}, where we provide details on the year of the main publication, the languages evaluated, as well as denoting whether or not entity recognition is supported\footnote{Some systems assume that mentions have previously been extracted from the text and are given as input, thereafter focusing only on the disambiguation process.}, and whether or not a demo, source code or API is currently available.\footnote{We presented an earlier version of such a table in previous work~\cite{Rosales-MendezP17}.} As expected, a high-level inspection of the table shows that English is the most popularly-evaluated (and thus we surmise supported) language, followed by European languages such as German, Spanish, French, Dutch and Italian. We also highlight that most of the multilingual EL approaches included in the table have emerged since 2011.

\begin{table}[t]
	\centering
	\caption{Overview of multilingual EL approaches; the italicised approaches will be incorporated as part of our experiments.}
	\label{tab:multilingual_approaches}
	\setlength{\tabcolsep}{3pt}
	\resizebox{\textwidth}{!}{
	\begin{tabular}{lcccccr}
		\toprule
		\textbf{Name} &  \textbf{Year} & \textbf{Evaluated Languages} & \textbf{ER} & \textbf{Demo} & \textbf{Src} & \textbf{API}\\ \midrule
		
		KIM \cite{KIM-popov2004kim} & 2004 &EN,FR,ES&\cmark&\cmark&\xmark&\cmark\\\midrule
        
        \textit{TagME} \cite{ferragina2010tagme} & 2010 & DE,EN,NL &\cmark&\cmark&\xmark&\cmark\\\midrule
		
		SDA \cite{SDA-charton2011automatic} & 2011 &EN,FR&\cmark&\xmark&\xmark&\xmark\\\midrule
		
		ualberta \cite{guo2012ualberta}& 2012 &EN,ZH&\cmark&\xmark&\xmark&\xmark\\\midrule
		
		HITS \cite{fahrni2012hits} & 2012 & EN,ES,ZH &\cmark&\xmark&\xmark&\xmark\\\midrule
		
		\textit{THD} \cite{THD-dojchinovski2012recognizing}  & 2012 &DE,EN,NL &\cmark&\cmark&\cmark&\cmark\\\midrule 
		
		\textit{DBpedia Spotlight} \cite{mendes2011dbpedia,daiber2013improving} & 2013  & DA,DE,EN,ES,FR,HU,IT,NL,RU &\cmark&\cmark&\cmark&\cmark\\\midrule
		
		Wang-Tang \cite{wang2013boosting} & 2013 & EN,ZH &\cmark&\xmark&\xmark&\xmark\\\midrule
        
        AGDISTIS \cite{usbeck2014agdistis}& 2014 & DE,EN&\xmark&\cmark&\cmark&\cmark\\\midrule
		
		\textit{Babelfy} \cite{Babelfy-moro2014entity}& 2014 & DE,EN,ES,FR,IT &\cmark&\cmark&\xmark&\cmark\\\midrule
		
		\textit{FREME}~\cite{freme-ner2016}&2016& DE,EN &\cmark&\xmark&\cmark&\cmark\\\midrule
		%& &French, Spanish, Russian&&&\\\midrule
		
		WikiME \cite{Cross-Lingual-Wikifier-tsai2016cross} & 2016 & AR,DE,EN,ES,FR,HE,IT,TA,TH,TL,TR,UR,ZH&\cmark&\cmark&\xmark&\xmark\\\midrule		
		
		FEL~\cite{FEL-pappu2017lightweight}& 2017 &EN,ES,ZH&\cmark&\xmark&\cmark&\xmark\\\midrule
        
		FOX~\cite{fox2017}&2017&DE,EN,ES,FR,NL&\cmark&\cmark&\cmark&\cmark\\\midrule
		%& & French, Dutch &&&\\
        
        MAG \cite{mag2017}& 2017 & DE,EN,ES,FR,IT,JA,NL&\xmark&\cmark&\cmark&\cmark\\
		
		%&2016&IDIOMAS&\cmark&\cmark&\cmark\\
		%& & French, Dutch &&&\\
		\bottomrule
	\end{tabular}
}
\end{table}

We will later conduct experiments using the GERBIL evaluation framework~\cite{gerbil-2015}, which allows for invoking and integrating the results of a variety of public APIs for EL, generating results according to standard metrics in a consistent manner. Hence, in our later experiments, we shall only consider those systems with a working REST-API made available by the authors of the system. In addition, we will manually label our \textsc{VoxEL} system according to Wikipedia, with which other important KBs such as DBpedia, YAGO, Freebase, Wikidata, etc., can be linked; hence we only include systems that support such a KB linked with Wikipedia. Note that GERBIL automatically takes care of mapping coreferent identifiers across KBs (and even across languages in cases such as DBpedia with different KB identifiers for different languages with cross-language links). 

With these criteria in mind, we experiment with the following systems: 

\begin{description}
\item[TagME (2010)] uses analyses of anchor texts in Wikipedia pages to perform EL~\cite{ferragina2010tagme}. The ranking stage is based primarily on two measures: \textit{commonness}, which describes how often an anchor text is associated with a particular Wikipedia entity; and \textit{relatedness}, which is a co-citation measure indicating how frequently candidate entities for different mentions are linked from the same Wikipedia article. TagME is language agnostic: it can take advantage of the Wikipedia Search API to apply the same conceptual process over different language versions of Wikipedia to support multilingual EL.
\item[THD (2012)] is based on three measures~\cite{THD-dojchinovski2012recognizing}: \textit{most frequent senses}, which ranks candidates for a mention based on the Wikipedia Search API results for that mention; \textit{co-occurrence}, which is a co-citation measure looking at how often candidate entities for different mentions are linked from the same paragraphs in Wikipedia; and \textit{explicit semantic analysis}, which uses keyword similarity measures to relate mentions with a concept. These methods are language agnostic and applicable to different language versions of Wikipedia.
\item[DBpedia Spotlight (2013)] was first proposed to deal with English annotations~\cite{mendes2011dbpedia}, based on keyword and string matching functions ranked by a probabilistic model based on a variant of a TF--IDF measure. DBpedia Spotlight is largely language-agnostic, where an extended version later proposed by Daiber et al.~\cite{daiber2013improving} leverages the multilingual information of the Wikipedia and DBpedia KBs to support multiple languages.
%\item[\textcolor{red}{\st{AGDISTIS (2014)}}] \textcolor{red}{\st{assumes that recognition has been performed using another tool and thus, given a set of mentions, focuses on the disambiguation process}}~\cite{usbeck2014agdistis}. \textcolor{red}{\st{The generation of candidates is mainly performed over indexes computed off-line from the target KB, where the ranking stage computes an assignment of links from related entities in a graph built over neighbouring candidate entities and mentions. A recent study}} \cite{mag2017} \textcolor{red}{\st{extends this approach, adding some new features to improve its behavior in multilingual scenarios.}} 
\item[Babelfy (2014)] performs EL with respect to a custom multilingual KB BabelNet~\footnote{\url{http://babelnet.org/}; April 1st, 2018} constructed from Wikipedia and WordNet, using machine translation to bridge the gaps in information available for different language versions of Wikipedia~\cite{Babelfy-moro2014entity}. Recognition is based on POS tagging for different languages, selecting candidate entities by string matching. Ranking is reduced to finding the densest subgraph that relates neighbouring entities and mentions.
\item[FREME (2016)] delegates the recognition of entities to the Stanford-NER tool, which is trained over the anchor texts of Wikipedia corpora in different languages. Candidate entities are generated by keyword search over local indexes, which are then ranked based on the number of matching anchor texts in Wikipedia linking to the corresponding article of the candidate entity~\cite{freme-ner2016}.
%\item[WikiME (2016)] uses a model based on word embedding, which includes a final step for each foreign language embeddings of projection to the English one.
\end{description}

With respect to FOX, note that while it meets all of our criteria, at the time or writing, we did not succeed in getting the API to run over VoxEL without error; hence we do not include this system. We also omit AGDISTIS and MAG from our selection because they do not perform recognition, requiring a prior identification of the entities in the input text (finding a suitable NER tool/model is not straightforward for some of the languages in our dataset).




\subsection{Multilingual EL Datasets}
%.................
%3) HABLAR SOBRE LOS corpus actuales monolingues

In order to train and evaluate EL approaches, labelled datasets -- annotated with the correct entity mentions and their respective KB links -- are essential. In some cases these datasets are labelled manually, while in other cases labels can be derived from existing information, such as anchor texts. In Table \ref{tab:datasets} we survey the labelled datasets most frequently used by EL approaches (note that sentence counts were not available for some datasets).

\newcommand{\ccell}[1]{\multicolumn{1}{c}{#1}}
\setlength{\tabcolsep}{1.2ex}
\begin{table}[tb!]
\centering

\caption{Survey of dataset for EL task. For multilingual datasets, the quantities shown refer to the English data available. We present metadata about the relaxed and strict version of our dataset by VoxEL$_R$ and VoxEL$_S$ respectively. (Abbreviations: $|D|$ number of documents, $|S|$ number of sentences, $|E|$ number of entities, \textbf{Mn} denotes that all entities were manually annotated.)}
\label{tab:datasets} 
\resizebox{\textwidth}{!}{
\begin{tabular}{lrrrcc}
\toprule
\textbf{Dataset}~~~~~~~~~~~~~~~~~~ & \ccell{$|D|$} & \ccell{$|S|$} & \ccell{$|E|$} & \ccell{\textbf{Mn}} & \ccell{\textbf{Languages}}\\\midrule
AIDA/CoNLL-Complete~\cite{aida2011} &1393    &22,137 &34,929  &\cmark  &EN \\\midrule
%AIDA/CoNLL-Test A~\cite{aida2011}   &216     &3,466  &5,917   &\cmark  &EN \\\midrule
%AIDA/CoNLL-Test B~\cite{aida2011}   &231     &3,684  &5,616   &\cmark  &EN \\\midrule
%AIDA/CoNLL-Training~\cite{aida2011} &946     &14,987 &23,396  &\cmark  &EN \\\midrule
KORE50~\cite{kore50}                &50      &50     &144     &\cmark  &EN \\\midrule
IITB~\cite{IITB2009}                &103     &1,781  &18,308  &\cmark &EN \\\midrule
ACE2004~\cite{aquaint}                &57      &-      &306     &\xmark &EN\\\midrule
%OKE challenge 2016                 &\xmark  &\cmark &\cmark  & &\xmark \\\midrule
AQUAINT~\cite{aquaint}              &50      &533    &727     &\xmark &EN \\\midrule
MSNBC~\cite{cucerzan2007large}                &20      &668    &747     &\xmark &EN \\\midrule
DBpedia Spotlight
\cite{mendes2011dbpedia}            &10      &58     &331     &\cmark &EN \\\midrule
N3-RSS 500~\cite{n3}                &1       &500    &1000    &\cmark  &EN \\\midrule
Reuters 128~\cite{n3}               &128     & -     &881     &\cmark  &EN \\\midrule
Wes2015~\cite{wes2015}              &331     & -     &28,586  &\cmark  & EN \\\midrule
%Derczynski                         &\xmark  &\xmark &\cmark  & &\cmark \\\midrule
News-100~\cite{n3}                  &100     &-      &1656    &\cmark  &DE \\\midrule
Thibaudet~\cite{renden2016}         &1       &3,807  &2,980   &\xmark  &FR \\\midrule
Bergson~\cite{renden2016}           &1       &4,280  &380     &\xmark  &FR \\\midrule
SemEval 2015 
Task 13~\cite{moro2015semeval}      &4       &137    &769     &\cmark &EN,ES,IT \\ \midrule
DBpedia Abstracts
~\cite{abstracts2016}               &39,132  &-      &505,033 &\xmark &DE,EN,ES,FR,IT,JA,NL \\\midrule
MEANTIME \cite{meantime2016}        &120     &597    &2,790   &\cmark &EN,ES,IT,NL \\\midrule 
VoxEL$_R$                           &15      &94     &674     &\cmark &DE,EN,ES,FR,IT\\\midrule  
VoxEL$_S$                           &15      &94     &204     &\cmark &DE,EN,ES,FR,IT\\ 
\bottomrule
\end{tabular}
}
\end{table}

We can see that the majority of datasets provide text in one language only -- predominantly English -- with the exceptions being as follows: 

\begin{description}
\item[SemEval 2015 Task 13:] is built over a biomedical, math, computer and social domain and is designed to support EL and WSD at the same time, containing annotations to Wikipedia, BabelNet and WordNet~\cite{moro2015semeval}.
\item[DBpedia Abstracts:] provides a large-scale training and evaluation corpora based on the anchor texts extracted from the abstracts (first paragraph) of Wikipedia pages in seven languages \cite{abstracts2016}.\footnote{\url{http://wiki-link.nlp2rdf.org/abstracts/}; April 1st, 2018} 
\item[MEANTIME:] consists of 120 news articles from WikiNews\footnote{\url{https://en.wikinews.org/}; April 1st, 2018} with manual annotations of entities, events, temporal information and semantic roles \cite{meantime2016}.\footnote{\url{http://www.newsreader-project.eu/results/data/wikinews/}; April 1st, 2018} 
\end{description}

%Amongst these multilingual datasets, we can highlight a number of shortcomings. First note that we do not include the 2013 TAC--KBP dataset in this list since it was not available at the time of writing. 

With respect to DBpedia Abstracts, while offering a very large multilingual corpus, the texts across different languages varies, as do the documents available; while such a dataset could be used to compare different systems for the same languages, it could not be used to compare the same systems for different languages. Furthermore, there are no guarantees for the completeness of the annotations since they are anchor texts/links extracted from Wikipedia; hence the dataset is best suited as a large collection of positive (training) examples, in a similar manner to how TagME~\cite{ferragina2010tagme} and FREME~\cite{freme-ner2016} use anchor texts.

Unlike DBpedia Abstracts, the SemEval and MEANTIME datasets contain analogous documents translated to different languages (also known as \textit{parallel corpora}~\cite{moro2015semeval}). Our \textsc{VoxEL} dataset complements these previous resources but with some added benefits. Primarily, both the SemEval and MEANTIME datasets exhibit slight variations in the annotations across languages, leading to (e.g.) a different number of entity annotations in the text for different languages; for example SemEval~\cite{moro2015semeval} reports 1,261 annotations for English, 1,239 for Spanish, and 1,225 for Italian, while MEANTIME~\cite{meantime2016} reports 2,790 entity mentions for English, 2,729 for Dutch, 2,709 for Italian and 2,704 for Spanish. On the other hand, \textsc{VoxEL} has precisely the same annotations across languages aligned at the sentence level, and also features datasets labelled under two definitions of entity. More generally, we see \textsc{VoxEL} as complementing these other datasets.\footnote{In previous work we used the SemEval dataset to compare EL systems for English and Spanish texts, where we refer the reader to~\cite{Rosales-MendezP17} for more details.}


%However, MEANTIME and SemEval 2015 Task 13 uses machine translation from English to obtain the text in the other languages. Despite the tremendous progress made in machine translation in recent years, translation errors are still a possibility, particularly where entity labels are involved. For example, while Google Translate would currently translate the Spanish sentence ``\textit{Vi la pel\'icula {\scriptsize$\ll$}Jungla de cristal{\scriptsize$\gg$ }ayer.}'' to ``\textit{I saw the movie `Crystal Jungle' yesterday.}'', a human expert would rather translate it as ``\textit{I saw the movie `Die Hard' yesterday.}''. 


%Involving more than one language is differently implemented by KBs. While Wikipedia separates the entities by languages, structured KBs such as Wikidata gather in the same multilingual resource all the information about each entity for all the languages supported. %BabelNet constitute other multilingual KB that follows this desirable property, constructed over Wikipedia but without the information conflict problems of it. The gap between the different editions of Wikipedia was filled in BabelNet mainly with automatic translation. 
%Having information gathered in this way allow EL systems to use the same link to annotate the same mentions in different languages, but in an environment like Wikipedia there are two ways make the annotations. For a given text input written in a specific language $L$, either the approaches target the entities of the version of the language $L$ of the KB (e.g., DBpedia Spotlight, AGDISTIS), or target the English version of the KB whatever the language $L$ is.%\textcolor{red}{We refer to the second ways of annotation in this paper as \textit{cross-lingual} links (e.g., Tagme, Babelfy).}

%However, MEANTIME and SemEval 2015 Task 13 use the automatic translation from English to obtain the text in the other languages. Despite the tremendous progress made in automatic translation in the last years, it can happen that it introduces translation errors. In this context, approaches based on grammar or any linguistic information could be devalued. 

%TOur dataset VoxEL is built over curted achiving the annotation through five languages.



%===========================================================================
\section{The VoxEL Dataset} \label{sec:voxel}

In this section, we describe the \textsc{VoxEL} Dataset that we propose as a gold standard for EL involving five languages: German, English, Spanish, French and Italian. \textsc{VoxEL} is based on 15 news articles sourced from the VoxEurop\footnote{\url{http://www.voxeurop.eu/}; April 1st, 2018} web-site: a European newsletter with the same news articles professionally translated to different languages. This source of text thus obviates the need for translation of texts to different languages, and facilitates the consistent identification and annotation of mentions (and their Wikipedia links) across languages. With VoxEL, we thus provide a high-quality resource with which to evaluate the behaviour of EL systems across a variety of European languages. 

While the VoxEurop newsletter is a valuable source of professionally translated text in several European languages, there are sometimes natural variations across languages that -- although they preserve meaning -- may change how the entities are mentioned. A common example is the use of pronouns rather than repeating a person's name to make the text more readable in a given language. Such variations would then lead to different entity annotations across languages, hindering comparability. Hence, in order to achieve the same number of sentences and annotations for each new (document), we applied small manual edits to homogenise the text (e.g., replacing a pronoun by a person's name). On the other hand, sentences that introduce new entities in one particular language, or that deviate too significantly across all languages, are eliminated; fewer than 10\% of the sentences from the original source were eliminated.

When labelling entities, we take into consideration the lack of consensus about what is an ``\textit{entity}''~\cite{usa_Gerbil_jha2017all,LingSW15,ourAMW2018}: some works conservatively consider only mentions of entities referring to fixed types such as person, organisation and location as entities (similar to the traditional NER/TAC consensus on an entity), while other authors note that a much more diverse set of entities are available in Wikipedia and related KBs for linking, and thus consider any noun-phrase mentioning an entity in Wikipedia to be a valid target for linking~\cite{PereraMAST16}. Furthermore, there is a lack of consensus on how overlapping entities -- like \textit{New York City Fire Department} -- should be treated~\cite{usa_Gerbil_jha2017all,LingSW15}; should \textit{New York City} be annotated as a separate entity or should we only cover maximal entities? Rather than take a stance on such questions -- which appear application dependant -- we instead create two versions of the data: a \textit{strict} version that considers only maximal entity mentions referring to persons, organisations and locations; and a \textit{relaxed} version that considers any noun phrase mentioning a Wikipedia entity as a mention, including overlapping mentions where applicable. For example, in the sentence \textit{``The European Central Bank released new inflation figures today''} the strict version would only include ``\textit{European Central Bank}'', while the relaxed version would also include ``\textit{Central Bank}'' and ``\textit{inflation}''.

%Taking into consideration the lack of consensus about \textit{``what is an entity?''} we propose handle two points of view of the annotations for the same input text. First, a \textit{relaxed} version that includes any Wikipedia page that is not disambiguation or redirection. Second, a \textit{strict} version that points only to irrefutable Wikipedia entities, and that are person, organisation or place. Thus we can measure the behavior of systems according to its application domain. Some systems have a general purpose and allow us to adapt to the application domain, for instance, DBpedia Spotlight allow us to specify the confidence and support parameters with use to decide which entity links. Although these two parameters allow adjustment to the context, they should be calibrated each time it changes. An idea closer to our objective is the behavior of Babelfy, which allows us to specify if we want to annotate only entities, or if we allow the inclusion of concepts.

To create the annotation of mentions with corresponding KB identifiers, we implemented a Web tool\footnote{\url{https://github.com/henryrosalesmendez/NIFify}; April 1st, 2018} that allows a user to annotate a text, producing output in the NLP Interchange Format (NIF)~\cite{HellmannLAB13}, as well as offering visualisations of the annotations that facilitate, e.g., revision. For each language, we provide annotated links that target the English Wikipedia entry, as well the language version of Wikipedia (if different from English). In case there was no appropriate Wikipedia entry for a mention of a person, organisation or place, we annotate the mention with a \url{NotInLexicon} marker. These annotations were created by the first author in English, which were then revised by the other authors according to the two labelling guidelines (\textit{strict} and \textit{relaxed}). The first author then extended these annotations to the other languages using the sentence-level correspondence, thereafter verifying that each language has the same number of annotations and the same set of English Wikipedia identifiers for each sentence.

In summary, \textsc{VoxEL} consists of 15 news articles (documents) from the multilingual newsletter VoxEurop, totaling 94 sentences; the central topic of these documents is politics, particularly at a European level. This text is annotated five times for each language, and two times for the strict and relaxed versions, giving a total of 150 annotated documents and 940 sentences. The same number of annotations is given for each language (including by sentence). For the strict version, each language has 204 annotated mentions, while for the relaxed version, each language has 674 annotated mentions. In the relaxed version, 6.2\%, 10.8\%, 20.3\% and 62.7\% of the entries correspond to \textit{persons}, \textit{organisations}, \textit{places} and \textit{others} respectively, while in the strict version the entities that fall in the first three classes constitute 16.9\%, 28.7\% and 54.4\% (\textit{others} are excluded by definition under the \textit{strict} guidelines). Again, this homogeneity of text and annotations across languages was non-trivial to achieve, but facilitates comparison of evaluation results not only across systems, but across languages. %For comparison, the SemEval dataset has 758, 768 and 784 annotations in the English, Spanish and Italian texts respectively, while MEANTIME has 2790, 2729, 2709 and 2704 mentions in the English, Dutch, Italian and Spanish texts.

%============================================================================
\section{Experiments}\label{sec:exp}

We now use our proposed \textsc{VoxEL} dataset to conduct experiments in order to explore the behaviour of state-of-the-art EL systems for multilingual settings. In particular, we are interested in the following questions:

\begin{itemize}
\item \textbf{RQ1}: How does the performance of systems compare for multilingual EL?
\item \textbf{RQ2}: For which of the five languages are the best results achieved?
\item \textbf{RQ3}: How would a method based on machine translation to English compare with directly configuring the system for a particular language?
\end{itemize}

In order to address \textbf{RQ1} and \textbf{RQ2}, we ran the multilingual EL systems Babelfy, DBpedia Spotlight, FREME, TagME and THD over both versions of \textsc{VoxEL} in all five languages. These experiments were conducted with the GERBIL~\cite{gerbil-2015} EL evaluation framework, which provides unified access to the public APIs of multiple EL tools, abstracting different input and output formats using the NIF vocabulary, translating identifiers across KBs, and allowing to apply standard metrics to measure the performance of results with respect to a labelled dataset. GERBIL calls these systems via their REST APIs maintaining default (non-language) parameters, except for the case of Babelfy, for which we analyse two configurations: one that applies a more liberal interpretation of entities to include conceptual entities (Babelfy$_R$), and another configuration that applies a stricter definition of entities (Babelfy$_S$), where the two configurations correspond loosely with the relaxed/strict versions of our dataset.


% best language
\newcommand{\bl}[1]{\textbf{#1}}

\begin{table}[tb!]
	\centering
	\caption{GERBIL Evaluation of EL systems with Micro Recall (\textit{mR}), Precision (\textit{mP}) and F$_1$ (\textit{mF}). A value ``--'' indicates that the system does not support the corresponding language. The results in bold are the best for that metric, system and dataset variant comparing across the five languages (i.e., the best in each row, split by Relax/Strict).}
	\label{tab:gerbil}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{@{}lcccccccccccc@{}}
			%\begin{tabular}{@{}lllllllllll@{}}
			\toprule
			&& \multicolumn{5}{c}{Relaxed}   & \multicolumn{5}{c}{Strict}  \\ \midrule
			&&~~DE~~~&~~EN~~~&~~ES~~~&~~FR~~~&~~IT~~~&~~DE~~~&~~EN~~~&~~ES~~~&~~FR~~~&~~IT~~~\\
			\cmidrule(lr){3-7}\cmidrule(lr){8-12}
                        &$mP$& \bl{0.840} & 0.649 & 0.835 & 0.824 & 0.810 & \bl{0.932} & 0.785 & 0.929 & 0.889 & 0.907 \\
			Babelfy$_R$ &$mR$& 0.461& 0.522 & \bl{0.549} & 0.488 & 0.451 & 0.676 & \bl{0.735} & 0.710 & 0.632 & 0.578 \\
                        &$mF$& 0.595& 0.578 & \bl{0.662} & 0.613 & 0.579 & 0.784 & 0.759 & \bl{0.805} & 0.739 & 0.706 \\\midrule
                        &$mP$& 0.903& 0.722 & \bl{0.916} & 0.912 & 0.884 & \bl{0.942} & 0.816 & 0.923 & 0.912 & 0.894 \\
			Babelfy$_S$ &$mR$& 0.181& \bl{0.219} & 0.210 & 0.200 & 0.192 & 0.558 & 0.524 & \bl{0.593} & 0.563 & 0.583 \\
                        &$mF$& 0.301& 0.336 & \bl{0.342} & 0.328 & 0.316 & 0.701 & 0.638 & \bl{0.722} & 0.697 & 0.706 \\\midrule
			%&$mP$& 0.313& 0.348 & 0.437 & 0.282 & \bl{0.512} & 0.568 & \bl{0.779} & 0.549 & 0.475 & 0.725 \\
			%AGDISTIS    &$mR$& 0.237& 0.265 & 0.329 & 0.210 & \bl{0.397} & 0.568 & \bl{0.779} & 0.549 & 0.475 & 0.725 \\
			%&$mF$& 0.270 & 0.301 & 0.376 & 0.241 & \bl{0.447} & 0.568 & \bl{0.779} & 0.549 & 0.475 & 0.725 \\\midrule
			&$mP$& 0.731& \bl{0.745} & 0.691 & 0.658 & 0.682 & 0.781 & \bl{0.854} & 0.690 & 0.691 & 0.800  \\
			DBspot      &$mR$& 0.508& \bl{0.577} & 0.399 & 0.360 & 0.488 & 0.544 & \bl{0.602} & 0.382 & 0.406 & 0.549  \\
			&$mF$& 0.600& \bl{0.650} & 0.506 & 0.466 & 0.569 & 0.641 & \bl{0.706} & 0.492 & 0.512 & 0.651 \\\midrule
			            &$mP$& 0.762 & 0.803 & 0.655 & 0.737 & \bl{0.857}&~ 0.750 & \bl{0.871}& 0.660 & 0.739 & 0.858  \\
			FREME       &$mR$& 0.161 & \bl{0.267}& 0.175 & 0.129 & 0.213 &~ 0.426 & \bl{0.764}& 0.553 & 0.416 & 0.652  \\
			            &$mF$& 0.266 & \bl{0.400}& 0.276 & 0.219 & 0.342 &~ 0.543 & \bl{0.814}& 0.602 & 0.532 & 0.740 \\\midrule
			&$mP$& 0.635& \bl{0.754} & --    & --    & 0.494 & 0.875 & \bl{0.946} & --    & --    & 0.742  \\
			TagME       &$mR$& 0.232& \bl{0.488} & --    & --    & 0.182 & 0.652 & \bl{0.784} & --    & --    & 0.509  \\
			&$mF$& 0.340& \bl{0.592} & --    & --    & 0.266 & 0.747 & \bl{0.857} & --    & --    & 0.604 \\\midrule
			&$mP$& \bl{0.831} & 0.806 & --    & --    & --    & \bl{0.857} & 0.809 & --    & --    & --    \\
			THD         &$mR$& 0.109& \bl{0.253} & --    & --    & --    & 0.352 & \bl{0.647} & --    & --    & --    \\
			&$mF$& 0.194& \bl{0.386} & --    & --    & --    & 0.500 & \bl{0.719} & --    & --    & --   \\\bottomrule 
		\end{tabular}
	}
\end{table}

The results of these experiments are shown in Table~\ref{tab:gerbil}, where we present micro-measures for Precision ($mP$), Recall ($mR$) and $F_1$ ($mF$), with all systems, for all languages, in both versions of the dataset.\footnote{The GERBIL results are available at \url{https://users.dcc.uchile.cl/~hrosales/ISWC2018_experiment_GERBIL.html}} From first impressions, we can observe that two systems -- TagME and THD -- do not support all languages, where we leave the corresponding results blank.

{\color{green}Aidan: I will revise the following when the results are fixed}

With respect to \textbf{RQ1}, for the Relaxed version, the highest $F_1$ scores are obtained by Babelfy$_R$ (0.662: ES) and DBpedia Spotlight (0.650: EN), which have comparable performance across languages. On the other hand, the highest $F_1$ scores for the Strict version are TagME (0.857: EN) and Babelfy$_S$ (0.805: ES). In general, the $F_1$ scores for the Strict version were higher than those for the Relaxed version: investigating further, the GERBIL framework only considers annotations to be false positives when a different annotation is given in the labelled dataset for an overlapping position; hence fewer labels in the Strict dataset will imply fewer false positives overall, which seems to outweigh the effect of the additional true positives that the Relaxed version would generate. Comparing the best Strict/Relaxed results for each system, we can see that Babelfy$_R$, DBpedia Spotlight and FREME have less of a gap between both, meaning that they tend to annotate a broader range of entities, while, in particular, Babelfy$_S$ and THD are more restrictive in the types of entities that they link.

With respect to \textbf{RQ2}, considering all systems, we can see a general trend that English had the best results overall, where it was always best for DBpedia Spotlight, FREME and TagME. For THD, German had higher precision, whereas English had higher recall. On the other hand, Babelfy generally had best results in German and Spanish, often having the \textit{lowest} precision in English. 

With respect to possible factors that explain such differences across languages, there are variations between languages that may make the EL task easier or harder depending on the features used; for example, systems that rely on capitalisation may perform differently for Spanish, which uses less capitalisation, (e.g., ``\textit{Jungla de cristal}'': a Spanish movie title in sentence case); and German, where all nouns are capitalised. Furthermore, the quality of EL resources available for different languages -- in terms of linguistic components, training sets, contextual corpora, KB meta-data, etc. -- may also vary across languages.
\medskip

Regarding \textbf{RQ3}, we will require another experiment to address the question of the efficacy of using machine translations. First we note that, although works in related areas -- such as cross-lingual ontology matching~\cite{FuBO10} -- have used machine translation to adapt to multilingual settings, to the best of our knowledge, no system listed in Table~\ref{tab:multilingual_approaches} uses machine translations over the input text (though systems such as Babelfy do use machine translations to enrich the lexical knowledge available in the KB). Hence we check to see if translating a text to English using a state-of-the-art approach -- Google Translate\footnote{\url{https://translate.google.com/}; April 1st, 2018} -- and applying EL over the translated English text would fare better than applying EL directly over the target language; we choose one target language to avoid generating results for a quadratic pairing of languages, and we choose English since it was the only language working for/supported by all systems in Table~\ref{tab:gerbil}.

A complication for these translation experiments is that while \textsc{VoxEL} contains annotations for the texts in their original five languages, including English, it does not contain annotations for the texts translated to English. While we considered manually annotating such documents produced by Google Translate, we opted against it partly due to the amount of labour it would again involve, but more importantly because it would be specific to one translation service at one point in time: as these translation services improve, these labelled documents would quickly become obsolete. Instead, we apply evaluation on a per-sentence basis, where for each sentence of a text in a non-English language, we translate it and then compare the set of annotations produced against the set of manually-annotated labels from the original English documents; in other words, we check the annotations produced by sentence, rather than by their exact position. This is only possible because in the original \textsc{VoxEL} dataset, we defined a one-to-one correspondence between sentences across languages. 

Note that since GERBIL requires labels to have a corresponding position, we thus needed to run these experiments locally outside of the GERBIL framework. Hence, for a sentence $s$, let $A$ denote the IRIs associated with manual labels for $s$ in the original English text, and let $B$ denote the IRIs annotated by the system for the corresponding sentence of the translated text; we denote true positives by $A \cap B$, false positives by $B - A$, and false negatives by $A - B$.\footnote{To compute Precision, Recall and $F_1$, we do not require true negatives.}

\newcommand{\blank}{\underline{\hspace{0.5em}}}

In Table \ref{tab:translations}, we show the results of this second experiment, focusing this time on the Micro-F$_1$ score obtained for each system over the five languages of \textsc{VoxEL}, again for the relaxed and strict versions. For each system, we consider three experiments: (1) the system is configured for the given language and run over text for the given language, (2) the system is configured for English and run over the text translated from the given language, (3) the system is configured for English and run over the text in the given language without translation. We use the third experiment to establish how the translation to English -- rather than the system configuration to English -- affects the results. First we note that without using positional information to check false positives (as per GERBIL), the results change from those presented in Table~\ref{tab:gerbil}; more generally, the gap between the Relaxed and Strict version is reduced. 

% best config
\newcommand{\bc}[1]{\ul{#1}}

\begin{table}[tb!]
\centering
\caption{Micro $F_1$ scores for systems performing EL with respect to the \textsc{VoxEL} dataset. For each system and each non-English language, we show the results of three experiments: first, for (\blank,\blank) the system is configured for the same language as the current text; second, for (EN,EN$_t$), the system is configured for English and applied to text translated to English from the original language; third, for (EN,\blank), the system is configured for English and run for the text in the current (original) language. Below the name of each system, we provide the relaxed and strict results for English text. Underlined results indicate the best of the three configurations for the given system, language and dataset variant (e.g., best for the columns of three values). Bold results indicate the best result for that system across all variations.}
\label{tab:translations}
%\begin{tabular}{@{}llllllllll@{}}
\resizebox{\textwidth}{!}{
\begin{tabular}{@{}llcccccccc@{}}
\toprule
&             & \multicolumn{4}{c}{Relaxed}     & \multicolumn{4}{c}{Strict}    \\ \midrule
&             &~~~DE~~~&~~~ES~~~&~~~FR~~~&~~~IT~~~&~~~DE~~~&~~~ES~~~&~~~FR~~~&~~~IT~~~  \\ \cmidrule(lr){3-6}\cmidrule(lr){7-10} 
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}Babelfy$_R$\\ (0.545,0.319)\end{tabular}}
& (\blank,\blank)     &\bc{0.523} &\bc{\bf 0.541}&0.493   &\bc{0.504} &\bc{0.344} &\bc{0.362} &0.309      &\bc{0.365} \\
& (EN,EN$_t$) &0.507      &0.515      &\bc{0.505} &0.501      &0.298      &0.298      &\bc{0.314} &0.301 \\
& (EN,\blank)     &0.215      &0.170      &0.195      &0.140      &0.253      &0.239      &0.220      &0.179 \\ \midrule
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}Babelfy$_S$\\ (0.308,0.567)\end{tabular}} 
& (\blank,\blank)     &0.279      &\bc{0.325} &0.290      &\bc{0.311} &\bc{0.572} &\bc{0.611} &\bc{0.583} &\bc{\bf 0.616} \\
& (EN,EN$_t$) &\bc{0.311} &0.309      &\bc{0.322} &0.303      &0.518      &0.523      &0.559      &0.532 \\
& (EN,\blank)     &0.201      &0.179      &0.189      &0.137      &0.376      &0.372      &0.395      &0.258 \\\midrule
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}DBpedia\\Spotlight\\(0.466,0.707)\end{tabular}}
& (\blank,\blank)     &0.400      &0.331      &0.240      &0.342      &0.510      &0.477      &0.481      &0.653 \\
& (EN,EN$_t$) &\bc{0.441}&\bc{0.454}&\bc{0.464}&\bc{0.449} &\bc{0.696} &\bc{0.694} &\bc{0.721}&\bc{\bf 0.729} \\
& (EN,\blank)     &0.209      &0.161      &0.18       &0.188      &0.374      &0.259      &0.326      &0.323 \\ \midrule
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}FREME\\ (0.407,0.708)\end{tabular}}
& (\blank,\blank)     &0.282      & 0.302      &0.268      &0.373      &0.483      &0.583      &0.479      &\bc{\bf 0.726}\\
& (EN,EN$_t$) &\bc{0.404} &\bc{0.403} &\bc{0.401} &\bc{0.408} &\bc{0.701} &\bc{0.713}&\bc{0.692} & 0.711\\
& (EN,\blank)     &0.166      &0.183      &0.196      &0.222      &0.190      &0.338      &0.342      &0.374\\ \midrule
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}TagME\\ (0.462,0.327)\end{tabular}}
& (\blank,\blank)     &0.414      &--         &--         & -         &0.272      &--         &--         &--    \\
& (EN,EN$_t$) &\bc{0.431} &\bc{\bf 0.450}&\bc{0.441}&\bc{0.439}&\bc{0.330}&\bc{0.333} &\bc{0.321} &\bc{0.336} \\
& (EN,\blank)     &0.188      &0.181      &0.200      &0.148      &0.212      &0.202      &0.197      &0.164 \\ \midrule
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}THD\\ (0.392,0.625)\end{tabular}}
& (\blank,\blank)     &0.241      &--         &--         &--         &0.546      &--         &--         &--    \\
& (EN,EN$_t$) &\bc{0.394} &\bc{0.392} &\bc{0.386} &\bc{0.387} &\bc{0.597} &\bc{0.620} &\bc{0.595} &\bc{\bf 0.623} \\
& (EN,\blank)     &0.207      &0.175      &0.217      &0.174      &0.251      &0.332      &0.403      &0.352 \\  
\bottomrule
\end{tabular}
}
\end{table}


%We underlined on in Table~\ref{tab:translations} for each system those scores that represent a better performance through automatic translation than with it own multilingual model. As we can observe, this happens for all the systems, at least for one of the languages.  In particular for DBpedia Spotlight this always happens. On the other hand, we also highlight with bold those scores that represent a better performance through automatic translation with respect the system configured for English over the English version, and we can see that the majority of these systems have this behavior according to VoxEL. So, this response RQ3, placing automatic translation as an option to tackle multilingual EL from systems with missing languages in their configuration as is the case of TagME and THD in this experiment. 

With respect to \textbf{RQ3}, in Table~\ref{tab:translations}, for each system, language and dataset variant, we underline which of the three configurations performs best. For example, in DBpedia Spotlight, all values on the (EN,EN$_t$) line -- which denotes applying DBpedia Spotlight configured for English over text translated to English -- are underlined, meaning that for all languages, prior translation to English outperformed submitting the text in its original language to DBpedia Spotlight configured for that language.\footnote{$\ldots$ it also implies that it outperforms running English EL on text in the original language, though this is hardly surprising and just presented for reference.}
In fact, for almost all systems, translating the input text to English generally outperforms using the available language configurations of the respective EL systems, with the exception of Babelfy, where the available multilingual settings generally outperforms the prior translation to English (we may recall that in Table~\ref{tab:gerbil}, Babelfy performed best for texts other than English). We further note that the translation results are generally competitive with those for the original English text -- shown below the name of the system for the Relaxed and Strict datasets -- even slightly outperforming those results in some cases. We also observe from the generally poor (EN,\blank) results that translation is important; in other words, one cannot simply just apply an EL system configured for English over another language and expect good results.

To give a better impression of the results obtained from the second experiment, in Figure~\ref{fig:bars}, for the selected systems, we show the following aggregations: (1) \textit{Calibrated}: the mean Micro-$F_1$ score across the four non-English languages with the EL system configured for that language; (2) \textit{Translation}: the mean Micro-$F_1$ score across the four non-English languages with the text translated to English and the EL system configured for English; (3) \text{English}, which presents the (single) Micro-$F_1$ score for the original English text. From this figure, we can see visually that translation is comparable to native English EL, and that translation often considerably outperforms EL in the original language. 

We highlight that using translation to English, the result will be an annotated text in English rather than the original language. However, given that translation is done per-sentence, the EL annotations for the translated English text could potentially be ``mapped'' back per sentence to the text in the original language; at the very least, the translated English annotations would be a useful reference.

\begin{figure}[t]
\resizebox{\textwidth}{!}{
	\begin{tikzpicture} 
	\begin{axis}[ 
	   title=(a) Relaxed,every axis title/.style={below right,at={(0.5,1)},draw=black,fill=white},
	   ybar, 
	   enlarge x limits=0.15, 
	   bar width=0.15cm,
	   ymin=0,
	   ymax=1,
	   height=.4\textwidth,
	   width=.55\textwidth,
	   y label style={at={(0.08,0.5)}},
	   %legend style={at={(0.295,1)}, anchor=north,legend columns=-1}, 
	   ylabel={Micro-F$_1$ score}, 
       symbolic x coords={Babelfy$_r$,Babelfy$_s$,DBspot,FREME,TagME,THD}, 
	   xtick=data, 
	   %nodes near coords, 
	   %nodes near coords align={vertical},
	   x tick label style={rotate=45,anchor=east},
	   %title=(relax)
	 ] 
	 \addplot coordinates {(Babelfy$_r$,0.515) (Babelfy$_s$,0.301) (DBspot,0.328) (FREME,0.306) (TagME,0.414) (THD,0.241) };
	 \addplot coordinates {(Babelfy$_r$,0.507) (Babelfy$_s$,0.311) (DBspot,0.452) (FREME,0.404) (TagME,0.431) (THD,0.394) };
	 \addplot coordinates {(Babelfy$_r$,0.545) (Babelfy$_s$,0.308) (DBspot,0.466) (FREME,0.407) (TagME,0.462) (THD,0.392) };
	 %\legend{Calibrated,Translation,EN}
	 \end{axis} 
	\end{tikzpicture}
	%
	\begin{tikzpicture} 
	\begin{axis}[ 
	   title=(a) Strict,every axis title/.style={below right,at={(0.5,1)},draw=black,fill=white},
	   ybar, 
	   enlarge x limits=0.15, 
	   bar width=0.15cm,
	   ymin=0,
	   ymax=1,
	   height=.4\textwidth,
	   width=.55\textwidth,
	   y label style={at={(0.08,0.5)}},
	   %legend style={at={(0.295,1)}, anchor=north,legend columns=-1}, 
	   ylabel={Micro-F$_1$ score}, 
       symbolic x coords={Babelfy$_r$,Babelfy$_s$,DBspot,FREME,TagME,THD}, 
	   xtick=data, 
	   %nodes near coords, 
	   %nodes near coords align={vertical},
	   x tick label style={rotate=45,anchor=east},
	   legend columns = 3,
	   legend style={at={(1,1.3)}} 
	   %title=(relax)
	 ]
	 \addplot coordinates {(Babelfy$_r$,0.345) (Babelfy$_s$,0.595) (DBspot,0.530) (FREME,0.567) (TagME,0.272) (THD,0.546) };
	 \addplot coordinates {(Babelfy$_r$,0.302) (Babelfy$_s$,0.533) (DBspot,0.710) (FREME,0.704) (TagME,0.330) (THD,0.597) };
	 \addplot coordinates {(Babelfy$_r$,0.319) (Babelfy$_s$,0.567) (DBspot,0.707) (FREME,0.708) (TagME,0.327) (THD,0.625) };
	 \legend{Calibrated,Translation,English}
	 \end{axis} 
	\end{tikzpicture}
}
\caption{Summary of the Micro-F$_1$ results over \textsc{VoxEL} Relaxed/Strict for the translation experiments, comparing mean values for setting the EL system to the language of the text (\textit{Calibrated}), translating the text to English first (\textit{Translation}), and the corresponding $F_1$ score for EL over the original English text (\textit{English})}
\label{fig:bars}
\end{figure}


%===============================================================
\section{Conclusion}
\label{sec:conclusion}

While Entity Linking has traditionally focused on processing texts in English, in recent years there has been a growing trend towards developing techniques and systems that can support multiple languages. To support such research, in this paper we have described a new labelled dataset for multilingual EL, which we call \textsc{VoxEL}. The dataset contains 15 new articles in 5 different languages with 2 different criteria for labelling, resulting in a corpus of 150 manually-annotated news articles. In a Strict version of the dataset considering a core of entities, we derive 204 annotated mentions in each language, while in a Relaxed version of the dataset considering a broader range of entities described by Wikipedia, we derive 674 annotated mentions in each language. The \textsc{VoxEL} dataset is distinguished by having a one-to-one correspondence of sentences -- and annotated entities per sentence -- between languages. The dataset (in NIF) is available online under a CC-BY 4.0 licence: \url{https://dx.doi.org/10.6084/m9.figshare.6539675}.

We used the \textsc{VoxEL} dataset to conduct experiments comparing the performance of selected EL systems in a multilingual setting. We found that in general, Babelfy and DBpedia Spotlight performed the most consistently across languages. We also found that with the exception of Babelfy, EL systems performed best over English versions of the text. Next, we compared configuring the multilingual EL system for each non-English language versus applying a machine translation of the text to English and running the system in English; with the exception of Babelfy, we found that the machine translation approach outperformed configuring the system for a non-English language; even in the case of Babelfy, the translation sometimes performed better, while in others it remained competitive. This raises a key issue for research on multilingual EL: state-of-the-art machine translation is now reaching a point where we must ask if it is worth building dedicated multilingual EL systems, or if we should focus on EL for one language to which other languages can be machine translated. 


{\footnotesize
\paragraph{Acknowledgements} The work of Henry Rosales-M\'endez was supported by CONICYT-PCHA/Doctorado Nacional/2016-21160017. The work was also supported by the Millennium Institute for Foundational Research on Data (IMFD) and by Fondecyt Grant No.\ 1181896. We also thank Michael R\"oder for his considerable help with GERBIL.}

%
% ---- Bibliography ----
%
%\bibliographystyle{splncs}%splncs03}
%\bibliography{bibfile}

\bibliographystyle{splncs03}
\bibliography{bibfile}


%\begin{thebibliography}{99}
%%\bibitem{pdd2017electro_medical_kbs}
%%Wang, M., Zhang, J., Liu, J., Hu, W., Wang, S., Li, X., Liu, W. {PDD} {G}raph: {B}ridging Electronic Medical Records and Biomedical Knowledge Graphs via {E}ntity {L}inking. In ISWC, (2017)  219--227
%
%%\bibitem{UniProt2016kbbioinformatic}
%%UniProt Consortium. UniProt: the universal protein knowledgebase. Nucleic acids research, \textbf{45}(D1) (2016), D158--D169
%
%%\bibitem{flabase2015musickbs}
%%Oramas, S., Gómez, F., Gómez Gutiérrez, E., Mora, J. (2015). Flabase: Towards the creation of a flamenco music knowledge base. ISMIR (2015) 378--384
%
%\bibitem{Borrega2007}
%Borrega, O., Taul\'e, M., Mart\'i, M.A. What do we mean when we speak about Named Entities. In Proceedings of Corpus Linguistics, (2007)
%
%\bibitem{ourAMW2018}
%Rosales-M\'endez, H., Poblete, Barbara., Hogan, Aidan. What should Entity Linking link?. In AMW 2018
%
%\bibitem{Jha2017} 
%Jha, K., R\"oder, M., Ngomo, A. C. N. All that glitters is not gold–rule-based curation of reference datasets for named entity recognition and entity linking. In ESWC (2017) 305--320
%
%\bibitem{Babelfy-moro2014entity}
%Moro, A., Raganato, A., Navigli, R.: Entity linking meets word sense disambiguation: a unified approach. Trans. of the ACL \textbf{2} (2014) 231--244
%
%\bibitem{joinapproach2015}
%Gang Luo, Xiaojiang Huang, Chin-Yew Lin, and Zaiqing Nie. Joint named entity recognition and disambiguation. In Proc. EMNLP, 2015
%
%
%
%\bibitem{KIM-popov2004kim}
%Popov, B., Kiryakov, A., Ognyanoff, D., Manov, D., Kirilov, A.: KIM--a semantic platform for information extraction and retrieval. Natural Language Engineering \textbf{10}(3-4) (2004) 375--392
%
%\bibitem{SDA-charton2011automatic}
%Charton, E., Gagnon, M., Ozell, B.: Automatic semantic web annotation of named entities. In: Canadian Conference on Artificial Intelligence, Springer (2011) 74--85
%
%\bibitem{guo2012ualberta}
%Guo, Z., Xu, Y., de S{\'a} Mesquita, F., Barbosa, D., Kondrak, G.: ualberta at {TAC-KBP} 2012: English and cross-lingual entity linking. In: TAC. (2012)
%
%\bibitem{fahrni2012hits}
%Fahrni, A., G{\"o}ckel, T., Strube, M.: {HITS'} monolingual and cross-lingual entity linking system at {TAC} 2012: A joint approach. In: TAC, Citeseer (2012)
%
%\bibitem{THD-dojchinovski2012recognizing}
%Dojchinovski, M., Kliegr, T.: Recognizing, classifying and linking entities with {W}ikipedia and {DB}pedia. WIKT (2012) 41--44
%
%\bibitem{mendes2011dbpedia} 
%Mendes, P.N., Jakob, M., Garc{\'\i}a-Silva, A., Bizer, C.: {DB}pedia spotlight: shedding light on the web of documents. In: I-SEMANTICS, ACM (2011) 1--8
%
%\bibitem{daiber2013improving}
%Daiber, J., Jakob, M., Hokamp, C., Mendes, P.N.: Improving efficiency and accuracy in multilingual entity extraction. In: I-SEMANTICS, ACM (2013) 121--124
%
%\bibitem{ferragina2010tagme} 
%Ferragina, P., Scaiella, U.: Tagme: on-the-fly annotation of short text fragments (by Wikipedia entities). In: CIKM, ACM (2010) 1625--1628
%
%%\bibitem{narducci2013cross}
%%Narducci, F., Palmonari, M., Semeraro, G.: Cross-language semantic matching for discovering links to e-gov services in the {LOD C}loud. KNOW@ LOD \textbf{992} (2013) 21--32
%
%\bibitem{wang2013boosting}
%Wang, Z., Li, J., Tang, J.: Boosting cross-lingual knowledge linking via concept annotation. In: IJCAI. (2013) 2733--2739
%
%\bibitem{usbeck2014agdistis}
%Usbeck, R., Ngomo, A.C.N., R{\"o}der, M., Gerber, D., Coelho, S.A., Auer, S., Both, A.: {AGDISTIS}-graph-based disambiguation of named entities using linked data. In: ISWC, Springer (2014) 457--471
%
%\bibitem{Cross-Lingual-Wikifier-tsai2016cross}
%Tsai, C.T., Roth, D.: Cross-lingual wikification using multilingual embeddings. In: NAACL-HLT. (2016) 589--598
%
%\bibitem{FEL-pappu2017lightweight}
%Pappu, A., Blanco, R., Mehdad, Y., Stent, A., Thadani, K.: Lightweight multilingual entity extraction and linking. In: WSDM, ACM (2017) 365--374
%
%\bibitem{mag2017}
%Moussallem, D., Usbeck, R., R\"oeder, M., Ngomo, A. C. N. {MAG}: {A} Multilingual, Knowledge-base Agnostic and Deterministic Entity Linking Approach. {K-CAP} 2017 , ACM, (2017) 9:1--9:8
%
%\bibitem{fox2017}
%Speck, R., Ngomo, A. C. N. {E}nsemble Learning of Named Entity Recognition Algorithms using Multilayer Perceptron for the Multilingual Web of Data. In K-CAP, 2017
%
%\bibitem{freme-ner2016}
%Sasaki, F., Dojchinovski, M., Nehring, J. Chainable and Extendable Knowledge Integration Web Services. In ISWC, (2016) 89--101
%
%
%\bibitem{abstracts2016}
%Br\"ummer, M., Dojchinovski, M., Hellmann, S. DBpedia Abstracts: A Large-Scale, Open, Multilingual NLP Training Corpus. In LREC, (2016)
%
%\bibitem{aida2011}
%Hoffart, J., Yosef, M. A., Bordino, I., F\"urstenau, H., Pinkal, M., Spaniol, M., Taneva, B., Thater, S., Weikum, G. Robust disambiguation of named entities in text. In EMNLP (2011) 782--792
%
%\bibitem{kore50}
%Hoffart, J., Seufert, S., Nguyen, D. B., Theobald, M., Weikum, G. {KORE}: keyphrase overlap relatedness for entity disambiguation. In CIKM, 2012.
%
%\bibitem{IITB2009}
%Kulkarni, S., Singh, A., Ramakrishnan, G., Chakrabarti, S. Collective annotation of Wikipedia entities in web text. In SIGKDD, (2009) 457--466
%
%\bibitem{moro2015semeval} 
%Moro, A., Navigli, R.: {SemEval}-2015 {Task} 13: Multilingual all-words sense disambiguation and entity linking. In: SemEval@ NAACL-HLT. (2015) 288--297
%
%\bibitem{meantime2016}
%Minard, A. L., Speranza, M., Urizar, R., Altuna, B., van Erp, M. G. J., Schoen, A. M., van Son, C. M. MEANTIME, the NewsReader multilingual event and time corpus. In  2016
%
%\bibitem{MSNBC07}
%Cucerzan, S. Large-scale named entity disambiguation based on Wikipedia data. In EMNLP-CoNLL, 2007
%
%
%\bibitem{ace04}
%Ratinov, L., Roth, D., Downey, D., Anderson, M. Local and Global Algorithms for Disambiguation to Wikipedia. In Proceedings of the 49th Annual Meeting of the Association for Computational Linguistics: Human Language Technologies. ACL, (2011) 1375--1384
%
%\bibitem{ace04_old}
%Doddington, G. R., Mitchell, A., Przybocki, M. A., Ramshaw, L. A., Strassel, S., Weischedel, R. M. The Automatic Content Extraction (ACE) Program-Tasks, Data, and Evaluation. In LREC, 2 (2004)
%
%\bibitem{wes2015}
%Waitelonis, J., Exeler, C., Sack, H. Linked data enabled generalized vector space model to improve document retrieval. In NLP \& DBpedia 2015 workshop, 2015
%
%\bibitem{renden2016}  Brando, C., Frontini, F., and Ganascia, J. G. REDEN: Named Entity Linking in Digital Literary Editions Using Linked Data Sets. Complex Systems Informatics and Modeling Quarterly, (2016)\textbf{4}(7) 60--80
%
%
%\bibitem{n3}
%Röder, M., Usbeck, R., Hellmann, S., Gerber, D., Both, A. $N^3$-{A} Collection of Datasets for Named Entity Recognition and Disambiguation in the NLP Interchange Format. In LREC, (2014) 3529--3533
%
%\bibitem{aquaint}
%Milne, D.,Witten, I.H.: Learning to link with wikipedia. In CIKM, ACM (2008) 509--518
%
%\bibitem{nif2013}
%Hellmann, S., Lehmann, J., Auer, S., and Br\"ummer, M. Integrating NLP using linked data. In ISWC, (2013) 98–113
%
%\bibitem{gerbil2015}
%Usbeck, R. et al. GERBIL -- General Entity Annotation Benchmark Framework. In 24th WWW conference, 2015
%
%\bibitem{fu2010}
%B. Fu and R. Brennan. Cross-lingual ontology mapping and its use on the multilingual semantic web. In Proceedings of WWW Workshop on Multilingual Semantic Web, 2010.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\begin{comment}
%\begin{table}[tb!]
%\centering
%\caption{My caption}
%\label{my-label}
%\begin{tabular}{@{}lcccccccccc@{}}
%\toprule
%            & \multicolumn{2}{c}{DE} & \multicolumn{2}{c}{EN} & \multicolumn{2}{c}{ES} & \multicolumn{2}{c}{FR} & \multicolumn{2}{c}{IT} \\ \midrule
%            %& Relax~~   & Strict    & Relax~~   & Strict    & Relax~~   & Strict    & Relax~~   & Strict    & Relax~~   & Strict    
%            &~~~$R$~~~  &~~~$S$~~~   &~~~$R$~~~  &~~~$S$~~~   &~~~$R$~~~  &~~~$S$~~~   &~~~$R$~~~  &~~~$S$~~~   &~~~$R$~~~  &~~~$S$~~~    
%            \\ \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11} 
%Babelfy$_r$ & 0.595   & 0.784   & 0.578   & 0.759  & 0.662  & 0.805   & 0.613   & 0.739  & 0.579   & 0.706        \\
%Babelfy$_s$ & 0.301   & 0.701   & 0.336   & 0.638  & 0.342  & 0.722   & 0.328   & 0.697  & 0.316   & 0.334        \\
%AGDISTIS    & 0.270   & 0.568   & 0.301   & 0.779  & 0.376  & 0.549   & 0.241   & 0.475  & 0.447   & 0.725        \\
%DBspot      & 0.600   & 0.641   & 0.650   & 0.706  & 0.506  & 0.492   & 0.466   & 0.512  & 0.569   & 0.651        \\
%FREME-NER   & 0.err   & err     & 0.508   & 0.550  & err    & err     & err     & err    & err     & err        \\
%Tagme 2     & 0.340   & 0.747   & 0.592   & 0.857  & -      & -       & -       & -      & 0.266   & 0.604        \\
%THD         & 0.194   & 0.500   & 0.386   & 0.719  & -      & -       & -       & -      & -       & -          \\ \bottomrule
%\end{tabular}
%\end{table}
%
%
%
%\begin{table}[tb!]
%\centering
%\caption{Otra version de la tabla anterior para quedarnos con la que mas nos acomode}
%\label{tab:gerbil}
%\begin{tabular}{@{}lccccccccccc@{}}
%%\begin{tabular}{@{}lllllllllll@{}}
%\toprule
%            & \multicolumn{5}{c}{Relax}   & \multicolumn{5}{c}{Strict}  \\ \midrule
%            &~~DE~~~&~~EN~~~&~~ES~~~&~~FR~~~&~~IT~~~&~~DE~~~&~~EN~~~&~~ES~~~&~~FR~~~&~~IT~~~\\
%            \cmidrule(lr){2-6}\cmidrule(lr){7-11}
%Babelfy$_r$ & 0.595  & 0.578 & 0.662 & 0.613 & 0.579 & 0.784 & 0.759 & 0.805 & 0.739 & 0.706 \\
%Babelfy$_s$ & 0.301  & 0.336 & 0.342 & 0.328 & 0.316 & 0.701 & 0.638 & 0.722 & 0.697 & 0.334 \\
%AGDISTIS    & 0.270  & 0.301 & 0.376 & 0.241 & 0.447 & 0.568 & 0.779 & 0.549 & 0.475 & 0.725 \\
%DBspot      & 0.600  & 0.650 & 0.506 & 0.466 & 0.569 & 0.641 & 0.706 & 0.492 & 0.512 & 0.651 \\
%FREME NER   & $err$  & 0.508 & $err$ & $err$ & $err$ & $err$ & 0.550 & $err$ & $err$ & $err$ \\
%Tagme 2     & 0.340  & 0.592 & -     & -     & 0.266 & 0.747 & 0.857 & -     & -     & 0.604 \\
%THD         & 0.194  & 0.386 & -     & -     & -     & 0.500 & 0.719 & -     & -     & -   \\ \bottomrule
%\end{tabular}
%\end{table}
%\end{comment}

%\end{thebibliography}

\end{document} 
